On the specific recursive structure of iterated parametricity

### 2025-11-16 paper/paper.tex
paper: use uppercase for types
paper: use a nice begin cases

\usepackage{amsmath, amssymb, mathrsfs, wasysym, tikz, tikz-cd, lmodern, mathpazo, anyfontsize, xargs, environ, multirow, tabularx, caption, bookmark, booktabs, makecell, colortbl, minted, art.cls/colorpal, art.cls/ct, art.cls/sset, art.cls/lim, art.cls/joinargs}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[prefix=bonak]{art.cls/xkeymask}

@@

@@

\newcommandx{\frametype}[2][1,2]{\prim{frametype}[][#1][#2][][]}
\newcommandx{\layertype}[2][1,2]{\prim{layertype}[][#1][#2][][]}
\newcommandx{\paintingtype}[2][1,2]{\prim{paintingtype}[][#1][#2][][]}
\newcommandx{\restrftype}[2][1,2]{\prim{restrftype}[][#1][#2][][]}
\newcommandx{\restrltype}[2][1,2]{\prim{restrltype}[][#1][#2][][]}
\newcommandx{\restrptype}[2][1,2]{\prim{restrptype}[][#1][#2][][]}
\newcommandx{\cohftype}[2][1,2]{\prim{cohftype}[][#1][#2][][]}
\newcommandx{\cohltype}[2][1,2]{\prim{cohltype}[][#1][#2][][]}
\newcommandx{\cohptype}[2][1,2]{\prim{cohptype}[][#1][#2][][]}
\newcommandx{\cohttype}[2][1,2]{\prim{cohttype}[][#1][#2][][]}

\newcommandx{\deps}[2][1,2]{\prim{deps}[][#1][#2][][]}
\newcommandx{\fulldeps}[2][1,2]{\prim{fulldeps}[][#1][][][]}
\newcommandx{\depscohs}[2][1,2]{\prim{depscohs}[][#1][#2][][]}
\newcommandx{\fulldepscohs}[2][1,2]{\prim{fulldepscohs}[][#1][][][]}
\newcommandx{\depscoht}[2][1,2]{\prim{depscoht}[][#1][#2][][]}
\newcommandx{\fulldepscoht}[2][1,2]{\prim{fulldepscoht}[][#1][][][]}
\newcommandx{\depstype}[2][1,2]{\prim{depstype}[][#1][#2][][]}
\newcommandx{\fulldepstype}[2][1,2]{\prim{fulldepstype}[][#1][][][]}
\newcommandx{\depscohstype}[2][1,2]{\prim{depscohstype}[][#1][#2][][]}
\newcommandx{\fulldepscohstype}[2][1,2]{\prim{fulldepscohstype}[][#1][][][]}
\newcommandx{\depscohttype}[2][1,2]{\prim{depscohttype}[][#1][#2][][]}
\newcommandx{\fulldepscohttype}[2][1,2]{\prim{fulldepscohttype}[][#1][][][]}

@@

\begin{align*}
  \framep[n][p]   & : \U[m]                                                                                                     & \mbox{for all $p\leq n$} \\
  \painting[n][p] & : \framep[n][p] \rightarrow \U[m]                                                                           & \mbox{for all $p\leq n$} \\
  \restrf[n][p]   & : \Pi q \leq n+p.\, \Pi \epsilon.\, \framep[n+1][p] \rightarrow \framep[n][p]                                               & \mbox{for all $p\leq n$} \\
  \restrp[n][p]   & : \Pi q \leq n+p.\, \Pi \epsilon.\, \Pi d:\framep[n+1][p].\,                                                                                           \\
                  & \;\;\;\;\painting[n+1][p](d) \rightarrow \painting[n][p](\restrf[n][p](d))                                  & \mbox{for all $p\leq n$} \\
  \cohf[n][p]     & : \Pi qr\epsilon\omega.\, \restrf[n][p][\epsilon][q] \circ \restrf[n+1][p][\omega][r] =                                                \\
                  & \;\;\;\;\restrf[n][p][\omega][r] \circ \restrf[n+1][p][\epsilon][q+1]                                       & \mbox{for all $p\leq n$} \\
  \cohp[n][p]     & \Pi qr\epsilon\omega.\,\Pi d:\framep[n+2][p].\,\\
                  & \;\;\;\;\restrp[n][p][q][\epsilon](\restrf[n+1][p][r][\omega](d)) \circ \restrp[n+1][p][r][\omega](d) =                                \\
                  & \;\;\;\;\restrp[n][p][r][\omega](\restrf[n+1][p][q+1][\epsilon](d)) \circ \restrp[n+1][p][q+1][\epsilon](d) & \mbox{for all $p\leq n$} \\
\end{align*}

@@

\begin{align*}
  \framep[n][0,...,n-1]   & : \frametype[n][0,...,n-1]                         \\
  \painting[n][0,...,n-1] & : \paintingtype[n][0,...,n-1](\framep[n][0,...,n-1]) \\
  \restrf[n][0,...,n-1]   & : \restrftype[n][0,...,n-1]
    \left(\begin{array}{l}
              \framep[n][0,...,n-1]   \\
              \painting[n][0,...,n-1] \\
    \end{array}\right)                                            \\
  \restrp[n][0,...,n-1](E:\framep[n+1][n]
    \left(\begin{array}{l}
              \framep[n][0,...,n-1]   \\
              \painting[n][0,...,n-1] \\
              \restrf[n][0,...,n-1]   \\
    \end{array}\right)\rightarrow \U) & : \restrptype[n][0,...,n-1]
    \left(\begin{array}{l}
              \framep[n][0,...,n-1]   \\
              \painting[n][0,...,n-1] \\
              \restrf[n][0,...,n-1]   \\
              E\\
    \end{array}\right)                                            \\
  \cohf[n][0,...,n-1](E:\framep[n+1][n]
    \left(\begin{array}{l}
              \framep[n][0,...,n-1]   \\
              \painting[n][0,...,n-1] \\
              \restrf[n][0,...,n-1]   \\
    \end{array}\right)\rightarrow \U) & : \cohftype[n][0,...,n-1]
    \left(\begin{array}{l}
              \framep[n][0,...,n-1]   \\
              \painting[n][0,...,n-1] \\
              \restrf[n][0,...,n-1]   \\
              E\\
              \restrp[n][0,...,n-1]   \\
    \end{array}\right)                                            \\
    \cohp[n][0,...,n-1]
      \left(\begin{array}{l}
              E:\framep[n+1][n]
                \left(\begin{array}{l}
              \framep[n][0,...,n-1]   \\
              \painting[n][0,...,n-1] \\
              \restrf[n][0,...,n-1]   \\
        \end{array}\right)\rightarrow \U \\
              E':\framep[n+2][n+1](\overline{\deps}
              \left(\begin{array}{l}
              \framep[n][0,...,n-1]   \\
              \painting[n][0,...,n-1] \\
              \restrf[n][0,...,n-1]   \\
              E\\
              \restrp[n][0,...,n-1]   \\
              \cohf[n][0,...,n-1]   \\
        \end{array}\right))\rightarrow \U
      \end{array}\right)                                            \\
      & : \cohptype[n][0,...,n-1]
      \left(\begin{array}{l}
              \framep[n][0,...,n-1]   \\
              \painting[n][0,...,n-1] \\
              \restrf[n][0,...,n-1]   \\
              E\\
              \restrp[n][0,...,n-1]   \\
              \cohf[n][0,...,n-1]   \\
              E'\\
      \end{array}\right)                                            \\
\end{align*}

>>>>

\usepackage{amsmath, amssymb, mathrsfs, mathtools, wasysym, tikz, tikz-cd, lmodern, mathpazo, anyfontsize, xargs, environ, multirow, tabularx, caption, bookmark, booktabs, makecell, colortbl, minted, art.cls/colorpal, art.cls/ct, art.cls/sset, art.cls/lim, art.cls/joinargs}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[prefix=bonak]{art.cls/xkeymask}

@@

\newcommandx{\depsp}[8][2,3,4,5,6,7,8]{
  \ensuremath{\mathsf{\color{russian-green}{deps}}_{
    \joinargs[\mathsf{\color{indian-yellow}{#1}}][#2][#3][#4]}^{\joinargs[#5][#6][#7]}}
}

\newcommandx{\depstypep}[8][2,3,4,5,6,7,8]{
  \ensuremath{\mathsf{\color{russian-green}{DEPS}}_{
    \joinargs[\mathsf{\color{indian-yellow}{#1}}][#2][#3][#4]}^{\joinargs[#5][#6][#7]}}
}

@@

\newcommandx{\frametype}[2][1,2]{\prim{FRAME}[][#1][#2][][]}
\newcommandx{\layertype}[2][1,2]{\prim{LAYER}[][#1][#2][][]}
\newcommandx{\paintingtype}[2][1,2]{\prim{PAINTING}[][#1][#2][][]}
\newcommandx{\restrftype}[2][1,2]{\restr{FRAME}[][][][#1][#2][][]}
\newcommandx{\restrltype}[2][1,2]{\restr{LAYER}[][][][#1][#2][][]}
\newcommandx{\restrptype}[2][1,2]{\restr{PAINTING}[][][][#1][#2][][]}
\newcommandx{\cohftype}[2][1,2]{\coh{FRAME}[][][][][][#1,#2][][]}
\newcommandx{\cohltype}[2][1,2]{\coh{LAYER}[][][][][][#1,#2][][]}
\newcommandx{\cohptype}[2][1,2]{\coh{PAINTING}[][][][][][#1,#2][][]}
\newcommandx{\cohttype}[2][1,2]{\cohtwo{FRAME}[][][][][][#1,#2][][]}

\newcommandx{\deps}[2][1,2]{\depsp{}[][][][#1][#2][][]}
\newcommandx{\fulldeps}[1][1]{\depsp{full}[][][][#1][][][]}
\newcommandx{\depscohs}[2][1,2]{\depsp{cohs}[][][][#1][#2][][]}
\newcommandx{\fulldepscohs}[1][1]{\depsp{fullcohs}[][#1][][][]}
\newcommandx{\depscoht}[2][1,2]{\depsp{coht}[][][][#1][#2][][]}
\newcommandx{\fulldepscoht}[1][1]{\depsp{fullcoht}[][][][#1][][][]}
\newcommandx{\depstype}[2][1,2]{\depstypep{}[][][][#1][#2][][]}
\newcommandx{\fulldepstype}[2][1,2]{\depstypep{full}[][][][#1][][][]}
\newcommandx{\depscohstype}[2][1,2]{\depstypep{cohs}[][][][#1][#2][][]}
\newcommandx{\fulldepscohstype}[1][1]{\depstypep{fullcohs}[][][][#1][][][]}
\newcommandx{\depscohttype}[2][1,2]{\depstypep{coht}[][][][#1][#2][][]}
\newcommandx{\fulldepscohttype}[1][1]{\depstypep{fullcoht}[][][][#1][][][]}

@@

\begin{align*}
  \framep[n][p]   & : \U[m]                                                                                                     & \mbox{for all $p\leq n$} \\
  \painting[n][p] & : \framep[n][p] \rightarrow \U[m]                                                                           & \mbox{for all $p\leq n$} \\
  \restrf[n][p]   & : \Pi q \leq n+p.\, \Pi \epsilon.\, \framep[n+1][p] \rightarrow \framep[n][p]                               & \mbox{for all $p\leq n$} \\
  \restrp[n][p]   & : \Pi q \leq n+p.\, \Pi \epsilon.\, \Pi d:\framep[n+1][p].\,                                                                           \\
                  & \;\;\;\;\painting[n+1][p](d) \rightarrow \painting[n][p](\restrf[n][p](d))                                  & \mbox{for all $p\leq n$} \\
  \cohf[n][p]     & : \Pi qr\epsilon\omega.\, \restrf[n][p][\epsilon][q] \circ \restrf[n+1][p][\omega][r] =                                                \\
                  & \;\;\;\;\restrf[n][p][\omega][r] \circ \restrf[n+1][p][\epsilon][q+1]                                       & \mbox{for all $p\leq n$} \\
  \cohp[n][p]     & \Pi qr\epsilon\omega.\,\Pi d:\framep[n+2][p].\,                                                                                        \\
                  & \;\;\;\;\restrp[n][p][q][\epsilon](\restrf[n+1][p][r][\omega](d)) \circ \restrp[n+1][p][r][\omega](d) =                                \\
                  & \;\;\;\;\restrp[n][p][r][\omega](\restrf[n+1][p][q+1][\epsilon](d)) \circ \restrp[n+1][p][q+1][\epsilon](d) & \mbox{for all $p\leq n$} \\
\end{align*}

@@

\begin{align*}
  \depscohs[n][p]\begin{cases}
                   \deps[n][p]\begin{cases}
                 \framep[n][0,...,n-1]   & : \frametype[n][0,...,n-1]                           \\
                 \painting[n][0,...,n-1] & : \paintingtype[n][0,...,n-1](\framep[n][0,...,n-1]) \\
                 \restrf[n][0,...,n-1]   & : \restrftype[n][0,...,n-1]
                 \left(\begin{array}{l}
                \framep[n][0,...,n-1]   \\
                \painting[n][0,...,n-1] \\
              \end{array}\right)
               \end{cases} \\
                   \restrp[n][0,...,n-1](E:\framep[n+1][n]
                   \left(\begin{array}{l}
              \framep[n][0,...,n-1]   \\
              \painting[n][0,...,n-1] \\
              \restrf[n][0,...,n-1]   \\
            \end{array}\right)\rightarrow \U) & : \restrptype[n][0,...,n-1]
                   \left(\begin{array}{l}
              \framep[n][0,...,n-1]   \\
              \painting[n][0,...,n-1] \\
              \restrf[n][0,...,n-1]   \\
              E                       \\
            \end{array}\right)                                                             \\
                   \cohf[n][0,...,n-1](E:\framep[n+1][n]
                   \left(\begin{array}{l}
              \framep[n][0,...,n-1]   \\
              \painting[n][0,...,n-1] \\
              \restrf[n][0,...,n-1]   \\
            \end{array}\right)\rightarrow \U) & : \cohftype[n][0,...,n-1]
                   \left(\begin{array}{l}
              \framep[n][0,...,n-1]   \\
              \painting[n][0,...,n-1] \\
              \restrf[n][0,...,n-1]   \\
              E                       \\
              \restrp[n][0,...,n-1]   \\
            \end{array}\right)
                 \end{cases} \\
  \cohp[n][0,...,n-1]
  \left(\begin{array}{l}
            E:\framep[n+1][n]
            \left(\begin{array}{l}
                \framep[n][0,...,n-1]   \\
                \painting[n][0,...,n-1] \\
                \restrf[n][0,...,n-1]   \\
              \end{array}\right)\rightarrow \U \\
            E':\framep[n+2][n+1](\overline{\deps}
            \left(\begin{array}{l}
                \framep[n][0,...,n-1]   \\
                \painting[n][0,...,n-1] \\
                \restrf[n][0,...,n-1]   \\
                E                       \\
                \restrp[n][0,...,n-1]   \\
                \cohf[n][0,...,n-1]     \\
              \end{array}\right))\rightarrow \U
          \end{array}\right)
  : \cohptype[n][0,...,n-1]
  \left(\begin{array}{l}
            \framep[n][0,...,n-1]   \\
            \painting[n][0,...,n-1] \\
            \restrf[n][0,...,n-1]   \\
            E                       \\
            \restrp[n][0,...,n-1]   \\
            \cohf[n][0,...,n-1]     \\
            E'                      \\
          \end{array}\right)                                                                           \\
\end{align*}
